Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-07-16 Phase_II/draft/GAN.tex
edits

\section{Generative Adversarial Networks}
Generative Adversarial Networks (GANs) were introduced by \citep{goodfellow2014generative}. The underlying concept is straightforward: it involves two competing networks. The first network, known as the Generator, produces new images based on an input image. These will be referred to as generated images. The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth).

Through the alternating training of these networks, the generated images gradually become indistinguishable from the real images. Essentially, this process constitutes a two-player min-max game --- a classic problem in game theory. The original formulation of GANs is given by:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
where $V(D, G)$ denotes the value function of the min-max game.

@@

		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{data}} \left[ \log D^{*}_{G}(x) \right] \\ 

@@

where \(D^{*}_{G}\) denotes the optimum of the discriminator for a given fixed generator, as shown in equation (\ref{eq:Disc_optimum}). It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{data}\). Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{data}\). A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.

@@

	D^*_G(x) = \frac{p_{data}(x)}{p_{data}(x) + p_g(g)}

@@

	\includegraphics[width=\linewidth]{fig/ellipsoid_0.jpg}

@@

Subsequently, the GAN framework was extended to a conditional model \citep{mirza2014conditional}. In this formulation, both the Generator and the Discriminator receive additional information $y$, and the value function of the conditional GAN (cGAN) is expressed as:
\begin{equation}
	\centering
	\begin{aligned}
		V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x|y) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
	\end{aligned}
	\label{eq:conditional_GAN}
\end{equation}

\cite{isola2017image} further observed that combining the cGAN from equation \ref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth. Hence, the function that is minimized is:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(G)$ is given as
\begin{equation}
	\centering
	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}

This type of network has demonstrated remarkable robustness across a variety of applications. For example, it can generate colored images from grayscale inputs based on architectural labels, transform images from day to night, and even predict maps from satellite data. A more extensive list of applications is provided in \cite{isola2017image}.

@@

In contrast, the upsampling process uses only the standard Rectified Linear Unit (ReLU) for neuron activation. This stage also comprises convolutional layers followed by operations with a stride of 2 to upscale the image to a higher resolution. Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \cite{isola2017image}.

@@

\subsection{Discriminator}
As discussed earlier, the Discriminator is tasked with classifying the images produced by the Generator as either real or fake. It takes a real image from the dataset (often referred to as the target image for the Generator) and provides feedback to guide the Generator toward producing more accurate images. In this work, the PatchGAN model \cite{isola2017image} is employed as the Discriminator. Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.

>>>>

\section{Generative Adversarial Networks}
Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}. The underlying concept is straightforward: it involves two competing networks. The first network, known as the Generator, produces new images based on an input image. These will be referred to as generated images. The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth).

Through the alternating training of these networks, the generated images gradually become indistinguishable from the real images. Essentially, this process constitutes a two-player min-max game --- a classic problem in game theory. The original formulation of GANs is given by:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
where $V(D, G)$ denotes the value function of the min-max game.

@@

		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{\rm data}} \left[ \log D^{*}_{G}(x) \right] \\ 

@@

where \(D^{*}_{G}\) denotes the optimum of the discriminator for a given fixed generator, as shown in equation (\ref{eq:Disc_optimum}). It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{\rm data}\). Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{\rm data}\). A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.

@@

	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_g(g)}

@@

	\includegraphics[width=\linewidth]{fig/ellipse1612.jpg}

@@

Subsequently, the GAN framework was extended to a conditional model \citep{mirza2014conditional}. In this formulation, both the Generator and the Discriminator receive additional information $y$, and the value function of the conditional GAN (cGAN) is expressed as:
\begin{equation}
	\centering
	\begin{aligned}
		V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x|y) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
	\end{aligned}
	\label{eq:conditional_GAN}
\end{equation}
\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth. Hence, the function that is minimized is:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
with the choice $\lambda = 100$ and
\begin{equation}
	\centering
	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}
This type of network has demonstrated remarkable robustness across a variety of applications. For example, it can generate colored images from grayscale inputs based on architectural labels, transform images from day to night, and even predict maps from satellite data. A more extensive list of applications is provided in \cite{isola2017image}.

@@

In contrast, the upsampling process uses only the standard Rectified Linear Unit (ReLU) for neuron activation. This stage also comprises convolutional layers followed by operations with a stride of 2 to upscale the image to a higher resolution. Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \citep{isola2017image}.

@@

\subsection{Discriminator}
As discussed earlier, the Discriminator is tasked with classifying the images produced by the Generator as either real or fake. It takes a real image from the dataset (often referred to as the target image for the Generator) and provides feedback to guide the Generator toward producing more accurate images. In this work, the PatchGAN model \citep{isola2017image} is employed as the Discriminator. Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.

### 2025-07-16 Phase_II/draft/II.tex
colorbar
edits

\subsection{The signal for II}\label{sec:signal}
As a simple example, let us consider a pair of IACTs pointed at a star. Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively. The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.][]{acciari2020optical, dravins2013optical}
\begin{equation}
	g^{(2)}= \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
	\label{eqn:HBT}
\end{equation}
where $\tau$ is the time delay between the telescopes. For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.,][]{acciari2020optical}.
\begin{equation}
	g^{(2)} = 1 + \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eqn:HBT2}
\end{equation}
where $\Delta f$ is the electronic bandwidth of the photon detectors (which measure the intensities.  Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.  In eq.~(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution. For a uniform disk it is given by
\begin{equation}
 V_{12} = 2 \frac{J_1(\pi\theta_D b)}{(\pi\theta_D b)}
\label{eqn:absvisib}
\end{equation}
where $\theta_D$ is the angular diameter of the star and $b$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation. It is evident from eq.~(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter. However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$. In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
\begin{equation}
	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
\end{equation}
where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ denote the mean intensities from the two telescopes. Therefore, the signal measured by the photon detector in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational radiation, is
\begin{equation}
	c = g^{(2)} - 1 = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eq:signal}
\end{equation}
$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.

\subsection{The Signal-to-Noise Ratio for II}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/telescope.png}
	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
	\label{fig:teles}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/baseline.png}
	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
	\label{fig:base}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
	\label{fig:image}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
		\caption{The fourier transform of source.}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
		\caption{The logarithmic fourier transform of source.}
	\end{subfigure}
	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
	\label{fig:ft}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
		\caption{The fourier transform with baselines.}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
		\caption{The logarithmic fourier transform with baselines.}
	\end{subfigure}
	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}. The right panel shows the same on logarithmic scale}
	\label{fig:ft_base}
\end{figure*}
The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering. These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes (PMTs) \cite{aleksic2016major}. In the simulation model adopted here, we consider a set of four IACTs, each with similar properties. The positional configuration of these IACTs is shown in fig.~\ref{fig:teles}. The optical signal directed to a PMT is filtered using a spectral filter with a chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$. The use of filters not only reduces background noise but also improves the signal quality and the efficiency of the PMTs. Filtering background skylight becomes even more significant in II observations, as these are carried out during full moon nights. It is important to note that the light from the stellar source is focused on the PMT during II observations.

@@

\subsection{Baseline considerations}
The measurement of the size of stellar objects via absolute visibility depends on the distance between the telescopes, known as the baseline $d$.
\begin{equation}
	V_{12}(d) = \frac{c(d)}{c(0)}
	\label{eq:angular_size_meas}
\end{equation}
For achieving a good SNR with a given telescope configuration, covering as much as possible of the interferometric plane is always desirable. If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
\begin{equation}
	(u,v) = \frac{1}{\lambda} (d_E, d_N)
\end{equation}
where $d_E$ and $d_N$ are the baselines expressed in east and north coordinates. However, not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain. Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines. For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep[see e.g., eqs.~8--10 from][]{2020MNRAS.498.4577B}.
\begin{equation}
\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_E \\ d_N \\ d_A \\ \end{pmatrix}
	\label{eq:baseline_rot}
\end{equation}

Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (Fig.~\ref{fig:teles}) due to the Earth's rotation. Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as
\begin{equation}
	\label{eq:N_telescopes}
	\mathcal{N} = \tfrac12 N_T \cdot (N_T -1)
\end{equation}
where $N_T$ is the number of telescopes considered.
As the number of baselines increases non-linearly, Intensity Interferometry (II) benefits greatly from a large number of telescopes. The planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.

\subsection{Fast Rotating Stars: The Objects Considered}
In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN. Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}. Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, with brightness distributed across its surface. The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}. This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}. Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.

Intensity Interferometry counts the photons arriving at the telescopes from the stellar object. The correlation of these photon arrivals at the telescopes yields the squared visibility (explained in subsection~\ref{sec:signal}). This signal is the Fourier transform of the brightness distribution in the sky. Fig.\ref{fig:ft} represents the Fourier Transform of the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales. In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule. Therefore, we have simulated the II observation of a sky source over one night. Using this finite amount of signal from one night's observation, we have trained a Generative Adversarial Network (GAN) to construct the image of the source.

>>>>

\subsection{The signal for II}\label{sec:signal}
As a simple example, let us consider a pair of IACTs pointed at a star. Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively. The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.][]{acciari2020optical, 2013APh....43..331D}
\begin{equation}
	g^{(2)}= \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
	\label{eqn:HBT}
\end{equation}
where $\tau$ is the time delay between the telescopes. For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.,][]{acciari2020optical}.
\begin{equation}
	g^{(2)} = 1 + \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eqn:HBT2}
\end{equation}
where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities.  Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.  In eq.~(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution. For a uniform disk it is given by
\begin{equation}
 V_{12} = 2 \frac{J_1(\pi\theta_D b)}{(\pi\theta_D b)}
\label{eqn:absvisib}
\end{equation}
where $\theta_D$ is the angular diameter of the star and $b$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation. It is evident from eq.~(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter. However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$. In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
\begin{equation}
	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
\end{equation}
where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ denote the mean intensities from the two telescopes. Therefore, the signal measured by the photon detector in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational radiation, is
\begin{equation}
	c = g^{(2)} - 1 = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eq:signal}
\end{equation}
$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.

\subsection{The Signal-to-Noise Ratio for II}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/telescope.png}
	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
	\label{fig:teles}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/baseline.png}
	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
	\label{fig:base}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
	\label{fig:image}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
		\caption{The signal (absolute value of the Fourier transform of the source).}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
		\caption{The logarithm of the signal.}
	\end{subfigure}
	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum $(u, v)$ plane with the assumed telescope separations can be completed with the help of Earth rotation.}
	\label{fig:ft}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
		\caption{The signal as samples by the baselines.}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
		\caption{The logarithmic signal as sampled by the baselines.}
	\end{subfigure}
	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}. The right panel shows the same on logarithmic scale}
	\label{fig:ft_base}
\end{figure*}
The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering. These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes \citep[PMTs, see e.g.,][]{aleksic2016major}. In the simulation model adopted here, we consider a set of four IACTs, each with similar properties. The positional configuration of these IACTs is shown in Fig.~\ref{fig:teles}. The optical signal directed to a PMT is filtered using a spectral filter with a chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$. The use of filters not only reduces background noise but also improves the signal quality and the efficiency of the PMTs. Filtering background skylight becomes even more significant in II observations, as these are carried out during full moon nights. It is important to note that the light from the stellar source is focused on the PMT during II observations.

@@

\subsection{Baseline considerations}
The measurement of the size of stellar objects via absolute visibility depends on the distance between the telescopes, known as the baseline $d$.
\begin{equation}
	|V_{12}(d)|^2 = \frac{c(d)}{c(0)}
	\label{eq:angular_size_meas}
\end{equation}
For achieving a good SNR with a given telescope configuration, covering as much as possible of the interferometric plane is always desirable. If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
\begin{equation}
	(u,v) = \frac{1}{\lambda} (d_E, d_N)
\end{equation}
where $d_E$ and $d_N$ are the baselines expressed in east and north coordinates. However, of course sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain. Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines. For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep[see e.g., eqs.~8--10 from][]{2020MNRAS.498.4577B}.
\begin{equation}
\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_E \\ d_N \\ d_A \\ \end{pmatrix}
	\label{eq:baseline_rot}
\end{equation}

Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (Fig.~\ref{fig:teles}) due to the Earth's rotation. Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as
\begin{equation}
	\label{eq:N_telescopes}
	\mathcal{N} = \tfrac12 N_T \cdot (N_T -1)
\end{equation}
where $N_T$ is the number of telescopes considered.
As the number of baselines increases non-linearly, Intensity Interferometry (II) benefits greatly from a large number of telescopes. The CTAO can offer many more baselines --- \cite{2013APh....43..331D} considered the telescope configurations then being considered, and all provided dense coverage of the interferometric plane.

\subsection{Fast Rotating Stars: The Objects Considered}
In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN. Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}. Fig.~\ref{fig:image} shows a fictitious image qualitatively representing a fast-rotating star, with brightness distributed across its surface. The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}. This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}. Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.

Intensity Interferometry counts the photons arriving at the telescopes from the stellar object. The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}. Fig.\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales. In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule. Therefore, we have simulated the II observation of a sky source by four telescopes (correlated in pairs) over one night. Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
